The pollination trade-off

### 2018-12-03 paper/manuscript.Rmd
add key idea of discussion

>>>>

We found that the community context plays a central role at determining competition for pollination and in turn the quantity and quality of pollination. 
Although the factors that previous studies with a small number of species are identify as important, are still relevant at the community level, we identify some phenomena that may not be observable in systems with two or three species. 
Specifically, XX
